---
title: "Master 1 R Project"
date: "January 4, 2023"
output:
  html_document:
    toc: yes
    toc_float: yes
    keep_md: yes
    fig_caption: yes
    df_print: tibble
    fig_width: 8.5
    theme: readable
  html_notebook:
    fig_width: 10
    fig_caption: yes
    toc: yes
    theme: readable
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
```

# Comparative Analysis of the determinants of Economic growth in WAEMU and BRICS Countries from 2005 to 2018

**Performed by :**

-   GOMEZ Jean-Baptiste Boris
-   MOUSSA DJIBO Nabil
-   LAKSIBI Safae

This document presents a comparative analysis of the determinants of economic growth between two groups of countries which both experienced recession in 1980. The database was created using data from the World Bank website. After showing the growth gap between WAEMU countries and BRICS countries, we performed a **Im-Pesaran-Shin stationarity Test** to verify the stationarity of each of our variables. Then, after estimating the model and carrying out the **Hausman-Taylor Test**, we retained the Within model, i.e. the fixed effects model for the WAEMU countries and the error component model or random effects model for the BRICS countries. Finally, we performed the **Breush-Pagan heteroskedasticity test** and the **Durbin-Watson and Breusch-Godfrey/Wooldridge Autocorrelation of Error term test**.

## 1. Importing and Preparing Data

### 1.1 WAEMU Countries

Creation of the database of WAEMU countries The dataset is a database with many columns, so we use `pivot longer` to reduce the number of columns and have many rows. The degree of openness indicates the country's dependence on the outside and the place that the rest of the world holds in a country's economy. The formula for calculating the degree of trade openness is as follows: DO = [(Exports + Imports) / 2] / GDP) x 100.

```{r, echo=TRUE, message=FALSE, warning=FALSE}

library(foreign)
library(readxl)
library(dplyr)
library(tidyr)
library(ggplot2)
library(plotly)
library(plm)
library(stargazer)
library(car)
library(lmtest)

setwd("C:/Users/gomez/OneDrive/Documents/r STUDIO MASTER1/Project_R_M1/Databases")

######### Public expenses #############

data_DP <- read_excel("Depenses_publiques.xls", sheet = "Data", skip = 3) 
data_DP <- data_DP[,-3:-24]
names(data_DP)[1:2]<-c("Country_Name","Country_Code")
row_data_DP_UEMOA<- c("Bénin","Burkina Faso","Côte d'Ivoire","Guinée-Bissau","Mali","Niger","Sénégal","Togo")
data_DP_UEMOA<- data_DP[data_DP$Country_Name %in% row_data_DP_UEMOA,]
BenData_uemoa = data_DP_UEMOA[1,]
Depubdata <- BenData_uemoa %>% pivot_longer(c(3:ncol(data_DP_UEMOA)),names_to = "Year", values_to = "DEPUB")
tempdf = data.frame()
i=2
while (i<= nrow(data_DP_UEMOA) ) {
  tempdf<-data_DP_UEMOA[i,]
  tempdf<-tempdf %>% pivot_longer(c(3:ncol(data_DP_UEMOA)),names_to = "Year", values_to = "DEPUB")
  Depubdata <- rbind.data.frame(Depubdata,tempdf)
  i<-i+1
}

######### External Debts ###########

data_DEBTEXT <- read_excel("Dette_exterieur.xls", sheet = "Data", skip = 3) 
data_DEBTEXT <- data_DEBTEXT[,-3:-24]
names(data_DEBTEXT)[1:2]<-c("Country_Name","Country_Code")
row_data_DEBTEXT_UEMOA<- c("Bénin","Burkina Faso","Côte d'Ivoire","Guinée-Bissau","Mali","Niger","Sénégal","Togo")
data_DEBTEXT_UEMOA<- data_DEBTEXT[data_DEBTEXT$Country_Name %in% row_data_DEBTEXT_UEMOA,]
BenData_uemoa = data_DEBTEXT_UEMOA[1,]
Dettdata <- BenData_uemoa %>% pivot_longer(c(3:ncol(data_DEBTEXT_UEMOA)),names_to = "Year", values_to = "DEBTEXT") 
tempdf = data.frame()
i=2
while (i<= nrow(data_DEBTEXT_UEMOA) ) {
  tempdf<-data_DEBTEXT_UEMOA[i,]
  tempdf<-tempdf %>% pivot_longer(c(3:ncol(data_DEBTEXT_UEMOA)),names_to = "Year", values_to = "DEBTEXT")
  Dettdata <- rbind.data.frame(Dettdata,tempdf)
  i<-i+1
}

######### Gross savings ##############
data_Epar <- read_excel("epargne_brute.xls", sheet = "Data", skip = 3) 
data_Epar <- data_Epar[,-3:-24]
names(data_Epar)[1:2]<-c("Country_Name","Country_Code")
row_data_Epar_UEMOA<- c("Bénin","Burkina Faso","Côte d'Ivoire","Guinée-Bissau","Mali","Niger","Sénégal","Togo")
data_Epar_UEMOA<- data_Epar[data_Epar$Country_Name %in% row_data_Epar_UEMOA,]
BenData_uemoa = data_Epar_UEMOA[1,]
Epardata <- BenData_uemoa %>% pivot_longer(c(3:ncol(data_Epar_UEMOA)),names_to = "Year", values_to = "EPARBRUT") 
tempdf = data.frame()
i=2
while (i<= nrow(data_Epar_UEMOA) ) {
  tempdf<-data_Epar_UEMOA[i,]
  tempdf<-tempdf %>% pivot_longer(c(3:ncol(data_Epar_UEMOA)),names_to = "Year", values_to = "EPARBRUT")
  Epardata <- rbind.data.frame(Epardata,tempdf)
  i<-i+1
}

######### GDP per capita ##############

data_GDPH <- read_excel("GDPperHabitat.xls", sheet = "Data", skip = 3) 
data_GDPH <- data_GDPH[,-3:-24]
names(data_GDPH)[1:2]<-c("Country_Name","Country_Code")
row_data_GDPH_UEMOA<- c("Bénin","Burkina Faso","Côte d'Ivoire","Guinée-Bissau","Mali","Niger","Sénégal","Togo")
data_GDPH_UEMOA<- data_GDPH[data_GDPH$Country_Name %in% row_data_GDPH_UEMOA,]
BenData_uemoa = data_GDPH_UEMOA[1,]
GDPHdata <- BenData_uemoa %>% pivot_longer(c(3:ncol(data_GDPH_UEMOA)),names_to = "Year", values_to = "GDP_Habitat") 
tempdf = data.frame()
i=2
while (i<= nrow(data_GDPH_UEMOA) ) {
  tempdf<-data_GDPH_UEMOA[i,]
  tempdf<-tempdf %>% pivot_longer(c(3:ncol(data_GDPH_UEMOA)),names_to = "Year", values_to = "GDP_Habitat")
  GDPHdata <- rbind.data.frame(GDPHdata,tempdf)
  i<-i+1
}

######### Inflation in % GDP ##############

data_INFLA <- read_excel("inflation_deflateur_PIB.xls", sheet = "Data", skip = 3) 
data_INFLA <- data_INFLA[,-3:-24]
names(data_INFLA)[1:2]<-c("Country_Name","Country_Code")
row_data_INFLA_UEMOA<- c("Bénin","Burkina Faso","Côte d'Ivoire","Guinée-Bissau","Mali","Niger","Sénégal","Togo")
data_INFLA_UEMOA<- data_INFLA[data_INFLA$Country_Name %in% row_data_INFLA_UEMOA,]
BenData_uemoa = data_INFLA_UEMOA[1,]
INFLAdata <- BenData_uemoa %>% pivot_longer(c(3:ncol(data_INFLA_UEMOA)),names_to = "Year", values_to = "Inflation") 
tempdf = data.frame()
i=2
while (i<= nrow(data_INFLA_UEMOA) ) {
  tempdf<-data_INFLA_UEMOA[i,]
  tempdf<-tempdf %>% pivot_longer(c(3:ncol(data_INFLA_UEMOA)),names_to = "Year", values_to = "Inflation")
  INFLAdata <- rbind.data.frame(INFLAdata,tempdf)
  i<-i+1
}

######### Private investment ################

data_INVPR <- read_excel("Investissement_privée(FBCF).xls", sheet = "Data", skip = 3) 
data_INVPR <- data_INVPR[,-3:-24]
names(data_INVPR)[1:2]<-c("Country_Name","Country_Code")
row_data_INVPR_UEMOA<- c("Bénin","Burkina Faso","Côte d'Ivoire","Guinée-Bissau","Mali","Niger","Sénégal","Togo")
data_INVPR_UEMOA<- data_INVPR[data_INVPR$Country_Name %in% row_data_INVPR_UEMOA,]
BenData_uemoa = data_INVPR_UEMOA[1,]
INVPRdata <- BenData_uemoa %>% pivot_longer(c(3:ncol(data_INVPR_UEMOA)),names_to = "Year", values_to = "INPRIV") 
tempdf = data.frame()
i=2
while (i<= nrow(data_INVPR_UEMOA) ) {
  tempdf<-data_INVPR_UEMOA[i,]
  tempdf<-tempdf %>% pivot_longer(c(3:ncol(data_INVPR_UEMOA)),names_to = "Year", values_to = "INPRIV")
  INVPRdata <- rbind.data.frame(INVPRdata,tempdf)
  i<-i+1
}

######### Labour force ###############

data_POPACT <- read_excel("population_active.xls", sheet = "Data", skip = 3) 
data_POPACT <- data_POPACT[,-3:-24]
names(data_POPACT)[1:2]<-c("Country_Name","Country_Code")
row_data_POPACT_UEMOA<- c("Bénin","Burkina Faso","Côte d'Ivoire","Guinée-Bissau","Mali","Niger","Sénégal","Togo")
data_POPACT_UEMOA<- data_POPACT[data_POPACT$Country_Name %in% row_data_POPACT_UEMOA,]
BenData_uemoa = data_POPACT_UEMOA[1,]
POPACTdata <- BenData_uemoa %>% pivot_longer(c(3:ncol(data_POPACT_UEMOA)),names_to = "Year", values_to = "POP_ACT") 
tempdf = data.frame()
i=2
while (i<= nrow(data_POPACT_UEMOA) ) {
  tempdf<-data_POPACT_UEMOA[i,]
  tempdf<-tempdf %>% pivot_longer(c(3:ncol(data_POPACT_UEMOA)),names_to = "Year", values_to = "POP_ACT")
  POPACTdata <- rbind.data.frame(POPACTdata,tempdf)
  i<-i+1
}

######### Export of goods and services in GDP % ################

data_EXPIB <- read_excel("Exportation_de_bien_et_services_pourcentage_PIB.xls", sheet = "Data", skip = 3) 
data_EXPIB <- data_EXPIB[,-3:-24]
names(data_EXPIB)[1:2]<-c("Country_Name","Country_Code")
row_data_EXPIB_UEMOA<- c("Bénin","Burkina Faso","Côte d'Ivoire","Guinée-Bissau","Mali","Niger","Sénégal","Togo")
data_EXPIB_UEMOA<- data_EXPIB[data_EXPIB$Country_Name %in% row_data_EXPIB_UEMOA,]
BenData_uemoa = data_EXPIB_UEMOA[1,]
EXPIBdata <- BenData_uemoa %>% pivot_longer(c(3:ncol(data_EXPIB_UEMOA)),names_to = "Year", values_to = "EXP_PIB") 
tempdf = data.frame()
i=2
while (i<= nrow(data_EXPIB_UEMOA) ) {
  tempdf<-data_EXPIB_UEMOA[i,]
  tempdf<-tempdf %>% pivot_longer(c(3:ncol(data_EXPIB_UEMOA)),names_to = "Year", values_to = "EXP_PIB")
  EXPIBdata <- rbind.data.frame(EXPIBdata,tempdf)
  i<-i+1
}

######### Import of goods and services in GDP % ################

data_IMPIB <- read_excel("importation_des_biens_et_services_pourcentage_PIB.xls", sheet = "Data", skip = 3) 
data_IMPIB <- data_IMPIB[,-3:-24]
names(data_IMPIB)[1:2]<-c("Country_Name","Country_Code")
row_data_IMPIB_UEMOA<- c("Bénin","Burkina Faso","Côte d'Ivoire","Guinée-Bissau","Mali","Niger","Sénégal","Togo")
data_IMPIB_UEMOA<- data_IMPIB[data_IMPIB$Country_Name %in% row_data_IMPIB_UEMOA,]
BenData_uemoa = data_IMPIB_UEMOA[1,]
IMPIBdata <- BenData_uemoa %>% pivot_longer(c(3:ncol(data_IMPIB_UEMOA)),names_to = "Year", values_to = "IMP_PIB") 
tempdf = data.frame()
i=2
while (i<= nrow(data_IMPIB_UEMOA) ) {
  tempdf<-data_IMPIB_UEMOA[i,]
  tempdf<-tempdf %>% pivot_longer(c(3:ncol(data_IMPIB_UEMOA)),names_to = "Year", values_to = "IMP_PIB")
  IMPIBdata <- rbind.data.frame(IMPIBdata,tempdf)
  i<-i+1
}
############## The degree of openness #####################

OCdata <- cbind.data.frame(IMPIBdata, EXPIBdata[,ncol(EXPIBdata)])
OCdata[is.na(OCdata)] <- 0 # replace na  0 
OCdata$OUVCM <- (OCdata$IMP_PIB + OCdata$EXP_PIB)/2

# Merging dataset

Data_UEMOA <- cbind.data.frame(GDPHdata, POPACTdata[,ncol(POPACTdata)], INVPRdata[,ncol(INVPRdata)],
                               Epardata[,ncol(Epardata)], Dettdata[,ncol(Dettdata)], Depubdata[,ncol(Depubdata)],
                               OCdata["OUVCM"], INFLAdata[,ncol(INFLAdata)])

# Balanced panel data (2005 - 2018 without CIV) and without 2010 because Guinée-Bissau at negative value of brut saving irrelevant for log 

Data_UEMOA <- Data_UEMOA[Data_UEMOA$Country_Code != "CIV",]
Data_UEMOA <- Data_UEMOA[Data_UEMOA$Year %in% c(2005,2006,2007,2008,2009,2011,2012,2013,2014,2015,2016,2017,2018),]
Data_UEMOA <- Data_UEMOA %>% mutate_at(c('GDP_Habitat', 'POP_ACT', 'INPRIV', 'EPARBRUT', 'DEBTEXT', 'DEPUB', 'OUVCM', 'Inflation'), as.numeric)
Data_UEMOA$Code = as.factor(ifelse(Data_UEMOA$Country_Name == "Bénin",1,
                                   ifelse(Data_UEMOA$Country_Name == "Burkina Faso", 2,
                                          ifelse(Data_UEMOA$Country_Name == "Guinée-Bissau", 3,
                                                 ifelse(Data_UEMOA$Country_Name == "Mali", 4,
                                                        ifelse(Data_UEMOA$Country_Name == "Niger", 5,
                                                               ifelse(Data_UEMOA$Country_Name == "Sénégal", 6,7
                                                                            )))))))
Data_UEMOA %>% relocate(c("Code","Year"), .before = Country_Name) -> Data_UEMOA
Data_UEMOA <- as_tibble(Data_UEMOA)
Data_UEMOA
```

### 1.2 BRICS Countries

We do the same things for BRICS countries.

```{r, echo=TRUE, message=FALSE, warning=FALSE}
setwd("C:/Users/gomez/OneDrive/Documents/r STUDIO MASTER1/Project_R_M1/Databases")
######### Public expenses #############

data_DP <- read_excel("Depenses_publiques.xls", sheet = "Data", skip = 3) 
data_DP <- data_DP[,-3:-24]
names(data_DP)[1:2]<-c("Country_Name","Country_Code")
row_data_DP_BRICS<- c("Brésil","Fédération de Russie","Inde","Chine","Afrique du Sud")
data_DP_BRICS<- data_DP[data_DP$Country_Name %in% row_data_DP_BRICS,]
BenData_BRICS = data_DP_BRICS[1,]
Depubdata <- BenData_BRICS %>% pivot_longer(c(3:ncol(data_DP_BRICS)),names_to = "Year", values_to = "DEPUB") #gather(Year, DEPUB, 4:10)
tempdf = data.frame()
i=2
while (i<= nrow(data_DP_BRICS) ) {
  tempdf<-data_DP_BRICS[i,]
  tempdf<-tempdf %>% pivot_longer(c(3:ncol(data_DP_BRICS)),names_to = "Year", values_to = "DEPUB")
  Depubdata <- rbind.data.frame(Depubdata,tempdf)
  i<-i+1
}

######### External Debts ###########

data_DEBTEXT <- read_excel("Dette_exterieur.xls", sheet = "Data", skip = 3) 
data_DEBTEXT <- data_DEBTEXT[,-3:-24]
names(data_DEBTEXT)[1:2]<-c("Country_Name","Country_Code")
row_data_DEBTEXT_BRICS<- c("Brésil","Fédération de Russie","Inde","Chine","Afrique du Sud")
data_DEBTEXT_BRICS<- data_DEBTEXT[data_DEBTEXT$Country_Name %in% row_data_DEBTEXT_BRICS,]
BenData_BRICS = data_DEBTEXT_BRICS[1,]
Dettdata <- BenData_BRICS %>% pivot_longer(c(3:ncol(data_DEBTEXT_BRICS)),names_to = "Year", values_to = "DEBTEXT") 
tempdf = data.frame()
i=2
while (i<= nrow(data_DEBTEXT_BRICS) ) {
  tempdf<-data_DEBTEXT_BRICS[i,]
  tempdf<-tempdf %>% pivot_longer(c(3:ncol(data_DEBTEXT_BRICS)),names_to = "Year", values_to = "DEBTEXT")
  Dettdata <- rbind.data.frame(Dettdata,tempdf)
  i<-i+1
}

######### Gross savings ##############

data_Epar <- read_excel("epargne_brute.xls", sheet = "Data", skip = 3) 
data_Epar <- data_Epar[,-3:-24]
names(data_Epar)[1:2]<-c("Country_Name","Country_Code")
row_data_Epar_BRICS<- c("Brésil","Fédération de Russie","Inde","Chine","Afrique du Sud")
data_Epar_BRICS<- data_Epar[data_Epar$Country_Name %in% row_data_Epar_BRICS,]
BenData_BRICS = data_Epar_BRICS[1,]
Epardata <- BenData_BRICS %>% pivot_longer(c(3:ncol(data_Epar_BRICS)),names_to = "Year", values_to = "EPARBRUT") 
tempdf = data.frame()
i=2
while (i<= nrow(data_Epar_BRICS) ) {
  tempdf<-data_Epar_BRICS[i,]
  tempdf<-tempdf %>% pivot_longer(c(3:ncol(data_Epar_BRICS)),names_to = "Year", values_to = "EPARBRUT")
  Epardata <- rbind.data.frame(Epardata,tempdf)
  i<-i+1
}

######### GDP per capita ##############

data_GDPH <- read_excel("GDPperHabitat.xls", sheet = "Data", skip = 3) 
data_GDPH <- data_GDPH[,-3:-24]
names(data_GDPH)[1:2]<-c("Country_Name","Country_Code")
row_data_GDPH_BRICS<- c("Brésil","Fédération de Russie","Inde","Chine","Afrique du Sud")
data_GDPH_BRICS<- data_GDPH[data_GDPH$Country_Name %in% row_data_GDPH_BRICS,]
BenData_BRICS = data_GDPH_BRICS[1,]
GDPHdata <- BenData_BRICS %>% pivot_longer(c(3:ncol(data_GDPH_BRICS)),names_to = "Year", values_to = "GDP_Habitat") 
tempdf = data.frame()
i=2
while (i<= nrow(data_GDPH_BRICS) ) {
  tempdf<-data_GDPH_BRICS[i,]
  tempdf<-tempdf %>% pivot_longer(c(3:ncol(data_GDPH_BRICS)),names_to = "Year", values_to = "GDP_Habitat")
  GDPHdata <- rbind.data.frame(GDPHdata,tempdf)
  i<-i+1
}

######### Inflation in % GDP ##############

data_INFLA <- read_excel("inflation_deflateur_PIB.xls", sheet = "Data", skip = 3) 
data_INFLA <- data_INFLA[,-3:-24]
names(data_INFLA)[1:2]<-c("Country_Name","Country_Code")
row_data_INFLA_BRICS<- c("Brésil","Fédération de Russie","Inde","Chine","Afrique du Sud")
data_INFLA_BRICS<- data_INFLA[data_INFLA$Country_Name %in% row_data_INFLA_BRICS,]
BenData_BRICS = data_INFLA_BRICS[1,]
INFLAdata <- BenData_BRICS %>% pivot_longer(c(3:ncol(data_INFLA_BRICS)),names_to = "Year", values_to = "Inflation") 
tempdf = data.frame()
i=2
while (i<= nrow(data_INFLA_BRICS) ) {
  tempdf<-data_INFLA_BRICS[i,]
  tempdf<-tempdf %>% pivot_longer(c(3:ncol(data_INFLA_BRICS)),names_to = "Year", values_to = "Inflation")
  INFLAdata <- rbind.data.frame(INFLAdata,tempdf)
  i<-i+1
}

######### Private investment ################

data_INVPR <- read_excel("Investissement_privée(FBCF).xls", sheet = "Data", skip = 3) 
data_INVPR <- data_INVPR[,-3:-24]
names(data_INVPR)[1:2]<-c("Country_Name","Country_Code")
row_data_INVPR_BRICS<- c("Brésil","Fédération de Russie","Inde","Chine","Afrique du Sud")
data_INVPR_BRICS<- data_INVPR[data_INVPR$Country_Name %in% row_data_INVPR_BRICS,]
BenData_BRICS = data_INVPR_BRICS[1,]
INVPRdata <- BenData_BRICS %>% pivot_longer(c(3:ncol(data_INVPR_BRICS)),names_to = "Year", values_to = "INPRIV") 
tempdf = data.frame()
i=2
while (i<= nrow(data_INVPR_BRICS) ) {
  tempdf<-data_INVPR_BRICS[i,]
  tempdf<-tempdf %>% pivot_longer(c(3:ncol(data_INVPR_BRICS)),names_to = "Year", values_to = "INPRIV")
  INVPRdata <- rbind.data.frame(INVPRdata,tempdf)
  i<-i+1
}

######### Labour force ###############

data_POPACT <- read_excel("population_active.xls", sheet = "Data", skip = 3) 
data_POPACT <- data_POPACT[,-3:-24]
names(data_POPACT)[1:2]<-c("Country_Name","Country_Code")
row_data_POPACT_BRICS<- c("Brésil","Fédération de Russie","Inde","Chine","Afrique du Sud")
data_POPACT_BRICS<- data_POPACT[data_POPACT$Country_Name %in% row_data_POPACT_BRICS,]
BenData_BRICS = data_POPACT_BRICS[1,]
POPACTdata <- BenData_BRICS %>% pivot_longer(c(3:ncol(data_POPACT_BRICS)),names_to = "Year", values_to = "POP_ACT") 
tempdf = data.frame()
i=2
while (i<= nrow(data_POPACT_BRICS) ) {
  tempdf<-data_POPACT_BRICS[i,]
  tempdf<-tempdf %>% pivot_longer(c(3:ncol(data_POPACT_BRICS)),names_to = "Year", values_to = "POP_ACT")
  POPACTdata <- rbind.data.frame(POPACTdata,tempdf)
  i<-i+1
}

######### Export of goods and services in GDP % ################

data_EXPIB <- read_excel("Exportation_de_bien_et_services_pourcentage_PIB.xls", sheet = "Data", skip = 3) 
data_EXPIB <- data_EXPIB[,-3:-24]
names(data_EXPIB)[1:2]<-c("Country_Name","Country_Code")
row_data_EXPIB_BRICS<- c("Brésil","Fédération de Russie","Inde","Chine","Afrique du Sud")
data_EXPIB_BRICS<- data_EXPIB[data_EXPIB$Country_Name %in% row_data_EXPIB_BRICS,]
BenData_BRICS = data_EXPIB_BRICS[1,]
EXPIBdata <- BenData_BRICS %>% pivot_longer(c(3:ncol(data_EXPIB_BRICS)),names_to = "Year", values_to = "EXP_PIB") 
tempdf = data.frame()
i=2
while (i<= nrow(data_EXPIB_BRICS) ) {
  tempdf<-data_EXPIB_BRICS[i,]
  tempdf<-tempdf %>% pivot_longer(c(3:ncol(data_EXPIB_BRICS)),names_to = "Year", values_to = "EXP_PIB")
  EXPIBdata <- rbind.data.frame(EXPIBdata,tempdf)
  i<-i+1
}

######### Import of goods and services in GDP % ################

data_IMPIB <- read_excel("importation_des_biens_et_services_pourcentage_PIB.xls", sheet = "Data", skip = 3) 
data_IMPIB <- data_IMPIB[,-3:-24]
names(data_IMPIB)[1:2]<-c("Country_Name","Country_Code")
row_data_IMPIB_BRICS<- c("Brésil","Fédération de Russie","Inde","Chine","Afrique du Sud")
data_IMPIB_BRICS<- data_IMPIB[data_IMPIB$Country_Name %in% row_data_IMPIB_BRICS,]
BenData_BRICS = data_IMPIB_BRICS[1,]
IMPIBdata <- BenData_BRICS %>% pivot_longer(c(3:ncol(data_IMPIB_BRICS)),names_to = "Year", values_to = "IMP_PIB") 
tempdf = data.frame()
i=2
while (i<= nrow(data_IMPIB_BRICS) ) {
  tempdf<-data_IMPIB_BRICS[i,]
  tempdf<-tempdf %>% pivot_longer(c(3:ncol(data_IMPIB_BRICS)),names_to = "Year", values_to = "IMP_PIB")
  IMPIBdata <- rbind.data.frame(IMPIBdata,tempdf)
  i<-i+1
}

############## The degree of openness #####################

OCdata <- cbind.data.frame(IMPIBdata, EXPIBdata[,ncol(EXPIBdata)])
OCdata[is.na(OCdata)] <- 0 # replace NA to  0 
OCdata$OUVCM <- (OCdata$IMP_PIB + OCdata$EXP_PIB)/2

# Merging databases

Data_BRICS <- cbind.data.frame(GDPHdata, POPACTdata[,ncol(POPACTdata)], INVPRdata[,ncol(INVPRdata)],
                               Epardata[,ncol(Epardata)], Dettdata[,ncol(Dettdata)], Depubdata[,ncol(Depubdata)],
                               OCdata["OUVCM"], INFLAdata[,ncol(INFLAdata)])

# Balanced panel data (2005 - 2018 without CIV) and without 2010 because Guinée-Bissau at negative value of brut saving irrelevant for log 

Data_BRICS <- Data_BRICS[Data_BRICS$Country_Code != "CIV",]
Data_BRICS <- Data_BRICS[Data_BRICS$Year %in% c(2005,2006,2007,2008,2009,2011,2012,2013,2014,2015,2016,2017,2018),]
Data_BRICS <- Data_BRICS %>% mutate_at(c('GDP_Habitat', 'POP_ACT', 'INPRIV', 'EPARBRUT', 'DEBTEXT', 'DEPUB', 'OUVCM', 'Inflation'), as.numeric)
Data_BRICS$Code = as.factor(ifelse(Data_BRICS$Country_Name == "Afrique du Sud",1,
                                   ifelse(Data_BRICS$Country_Name == "Brésil", 2,
                                          ifelse(Data_BRICS$Country_Name == "Chine", 3,
                                                 ifelse(Data_BRICS$Country_Name == "Fédération de Russie", 4,5
                                                       )))))
Data_BRICS %>% relocate(c("Code","Year"), .before = Country_Name) -> Data_BRICS
Data_BRICS <- as_tibble(Data_BRICS)
Data_BRICS
```

## 2. Features of two Panels Databases

As we can see below our two databases are balanced panels. Concerning the characteristics of our two databases :

    | Countries Groups   | Number of individuals | Number of observations | Times series |
    |------------------- |:---------------------:|:----------------------:|-------------:|
    |        WAEMU       |           7           |           91           |      13      |
    |        BRICS       |           5           |           65           |      13      |

```{r, echo=TRUE, message=FALSE, warning=FALSE}
Data_UEMOA <- pdata.frame(Data_UEMOA, index = c("Country_Name", "Year"))
Data_UEMOA  %>%  is.pbalanced()

Data_BRICS <- pdata.frame(Data_BRICS, index = c("Country_Name", "Year"))
Data_BRICS  %>%  is.pbalanced()

pdim(Data_UEMOA)
pdim(Data_BRICS)
```

## 3. Comparing economic growth with GDP per capita between the two groups of countries by year

```{r echo=TRUE, message=FALSE, warning=FALSE}
df1 <- Data_UEMOA %>%
  group_by(Year) %>%
  summarise_at(vars(GDP_Habitat), list(Mean_GDPH = mean))

df2 <- Data_BRICS %>%
  group_by(Year) %>%
  summarise_at(vars(GDP_Habitat), list(Mean_GDPH = mean))

df1$Group_Name <- rep("WAEMU", times = nrow(df1))
df2$Group_Name <- rep("BRICS", times = nrow(df2))
Data_graph <- rbind(df1,df2)

ggplotly(ggplot(Data_graph,aes(x = Year, y =Mean_GDPH, fill = Group_Name)) + 
           geom_bar(stat = "identity", position = "dodge") + 
           scale_y_log10(expand = expansion(mult = c(0, 0.10))) + 
           scale_fill_manual(values=c("blue", "darkgreen")) +
           theme(panel.border = element_rect(linetype = "dashed", fill = NA)) +
           labs(x="Year",y="Mean GDP per Capita", caption = "Data source: World Bank data (2022).")+
           theme(legend.background = element_rect(fill="lightgray", 
                                                  size=0.3, linetype="solid"))+
           theme(legend.title = element_text(face = "bold"))+
           theme(plot.title = element_text(size = 8, face = "bold")) +
           ggtitle("Evolution of average GDP per capita (in dollars) in WAEMU and BRICS countries between 2005 and 2018"))
```

We performed a test for stationarity of the logarithmic variables and a descriptive analysis of stationary variables. Since inflation and trade openness are percentage variables, they will not be evaluated in logarithm.

```{r echo=TRUE, message=FALSE, warning=FALSE}
##### WAEMU
Data_UEMOA$GDP_Habitat <- log(Data_UEMOA$GDP_Habitat)
Data_UEMOA$POP_ACT <- log(Data_UEMOA$POP_ACT)
Data_UEMOA$INPRIV <- log(Data_UEMOA$INPRIV)
Data_UEMOA$EPARBRUT <- log(Data_UEMOA$EPARBRUT)
Data_UEMOA$DEBTEXT <- log(Data_UEMOA$DEBTEXT)
Data_UEMOA$DEPUB <- log(Data_UEMOA$DEPUB)

##### BRICS
Data_BRICS$GDP_Habitat <- log(Data_BRICS$GDP_Habitat)
Data_BRICS$POP_ACT <- log(Data_BRICS$POP_ACT)
Data_BRICS$INPRIV <- log(Data_BRICS$INPRIV)
Data_BRICS$EPARBRUT <- log(Data_BRICS$EPARBRUT)
Data_BRICS$DEBTEXT <- log(Data_BRICS$DEBTEXT)
Data_BRICS$DEPUB <- log(Data_BRICS$DEPUB)
```

## 4. Stationarity Test

### 4.1 Im-Pesaran-Shin Unit-Root Test

#### 4.1.1 WAEMU Countries

H0: There is unit root in variable or Variable is non stationarity significative level 5%

```{r echo=TRUE, message=FALSE, warning=FALSE}
GDP_Habitat_IPS <- data.frame(split(Data_UEMOA$GDP_Habitat, Data_UEMOA$Country_Name))
purtest(GDP_Habitat_IPS, pmax = 2, exo = "intercept", test = "ips")
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
POP_ACT_IPS <- data.frame(split(Data_UEMOA$POP_ACT, Data_UEMOA$Country_Name))
purtest(POP_ACT_IPS, pmax = 2, exo = "intercept", test = "ips")
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
INPRIV_IPS <- data.frame(split(Data_UEMOA$INPRIV, Data_UEMOA$Country_Name))
purtest(INPRIV_IPS, pmax = 2, exo = "intercept", test = "ips") 
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
EPARBRUT_IPS <- data.frame(split(Data_UEMOA$EPARBRUT, Data_UEMOA$Country_Name))
purtest(EPARBRUT_IPS, pmax = 2, exo = "intercept", test = "ips")
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
DEBTEXT_IPS <- data.frame(split(Data_UEMOA$DEBTEXT, Data_UEMOA$Country_Name))
purtest(DEBTEXT_IPS, pmax = 2, exo = "intercept", test = "ips") 
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
DEPUB_IPS <- data.frame(split(Data_UEMOA$DEPUB, Data_UEMOA$Country_Name))
purtest(DEPUB_IPS, pmax = 2, exo = "intercept", test = "ips")
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
OUVCM_IPS <- data.frame(split(Data_UEMOA$OUVCM, Data_UEMOA$Country_Name))
purtest(OUVCM_IPS, pmax = 2, exo = "intercept", test = "ips")
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
Inflation_IPS <- data.frame(split(Data_UEMOA$Inflation, Data_UEMOA$Country_Name))
purtest(Inflation_IPS, pmax = 2, exo = "intercept", test = "ips")
```

So WAEMU Non-Stationary variables : 'GDP_Habitat','POP_ACT', 'INPRIV', 'EPARBRUT', 'DEPUB' and 'DEBTEXT'.

#### 4.1.2 BRICS Countries

H0: There is unit root in variable or Variable is non stationarity significative level 5%

```{r echo=TRUE, message=FALSE, warning=FALSE}
GDP_Habitat_IPS <- data.frame(split(Data_BRICS$GDP_Habitat, Data_BRICS$Country_Name))
purtest(GDP_Habitat_IPS, pmax = 2, exo = "trend", test = "ips") 
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
POP_ACT_IPS <- data.frame(split(Data_BRICS$POP_ACT, Data_BRICS$Country_Name))
purtest(POP_ACT_IPS, pmax = 2, exo = "trend", test = "ips")   
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
INPRIV_IPS <- data.frame(split(Data_BRICS$INPRIV, Data_BRICS$Country_Name))
purtest(INPRIV_IPS, pmax = 2, exo = "trend", test = "ips")
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
EPARBRUT_IPS <- data.frame(split(Data_BRICS$EPARBRUT, Data_BRICS$Country_Name))
purtest(EPARBRUT_IPS, pmax = 2, exo = "trend", test = "ips")
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
DEBTEXT_IPS <- data.frame(split(Data_BRICS$DEBTEXT, Data_BRICS$Country_Name))
purtest(DEBTEXT_IPS, pmax = 2, exo = "trend", test = "ips") 
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
DEPUB_IPS <- data.frame(split(Data_BRICS$DEPUB, Data_BRICS$Country_Name))
purtest(DEPUB_IPS, pmax = 2, exo = "trend", test = "ips") 
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
OUVCM_IPS <- data.frame(split(Data_BRICS$OUVCM, Data_BRICS$Country_Name))
purtest(OUVCM_IPS, pmax = 2, exo = "trend", test = "ips")
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
Inflation_IPS <- data.frame(split(Data_BRICS$Inflation, Data_BRICS$Country_Name))
purtest(Inflation_IPS, pmax = 2, exo = "trend", test = "ips")
```

So BRICS Non-Stationary variables : 'GDP_Habitat','POP_ACT', 'INPRIV', 'EPARBRUT', 'DEPUB' and 'DEBTEXT'.

**Since the degree of trade openness (OUVCM) and inflation (Inflation) are stationary in the BRICS and WAEMU data, we will remove them from our model to keep only non-stationary variables in our model.**

```{r echo=TRUE, message=FALSE, warning=FALSE}
Data_UEMOA <- subset(Data_UEMOA, select = -c(OUVCM,Inflation))
Data_BRICS <- subset(Data_BRICS, select = -c(OUVCM,Inflation))
```

## 5. Descriptives Analysis on stationary variables

### 5.1 WAEMU Countries

```{r echo=TRUE, message=FALSE, warning=FALSE}
stargazer(Data_UEMOA, title="Descriptive Statistic ", type = "text")
```

**Boxplots**

```{r echo=TRUE, message=FALSE, warning=FALSE}
scatterplot(GDP_Habitat ~ Year | Country_Name, boxplot = FALSE,
            smooth = TRUE, reg.line = TRUE, data = Data_UEMOA)
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
scatterplot(POP_ACT ~ Year | Country_Name, boxplot = FALSE,
            smooth = TRUE, reg.line = TRUE, data = Data_UEMOA)
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
scatterplot(INPRIV ~ Year | Country_Name, boxplot = FALSE,
            smooth = TRUE, reg.line = TRUE, data = Data_UEMOA)
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
scatterplot(EPARBRUT ~ Year | Country_Name, boxplot = FALSE,
            smooth = TRUE, reg.line = TRUE, data = Data_UEMOA)
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
scatterplot(DEBTEXT ~ Year | Country_Name, boxplot = FALSE,
            smooth = TRUE, reg.line = TRUE, data = Data_UEMOA)
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
scatterplot(DEPUB ~ Year | Country_Name, boxplot = FALSE,
            smooth = TRUE, reg.line = TRUE, data = Data_UEMOA)
```

### 5.2 BRICS Countries

```{r echo=TRUE, message=FALSE, warning=FALSE}
stargazer(Data_BRICS, title="Descriptive Statistic ", type = "text")
```

**Boxplots**

```{r echo=TRUE, message=FALSE, warning=FALSE}
scatterplot(GDP_Habitat ~ Year | Country_Name, boxplot = FALSE,
            smooth = TRUE, reg.line = TRUE, data = Data_BRICS)
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
scatterplot(POP_ACT ~ Year | Country_Name, boxplot = FALSE,
            smooth = TRUE, reg.line = TRUE, data = Data_BRICS)
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
scatterplot(INPRIV ~ Year | Country_Name, boxplot = FALSE,
            smooth = TRUE, reg.line = TRUE, data = Data_BRICS)
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
scatterplot(EPARBRUT ~ Year | Country_Name, boxplot = FALSE,
            smooth = TRUE, reg.line = TRUE, data = Data_BRICS)
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
scatterplot(DEBTEXT ~ Year | Country_Name, boxplot = FALSE,
            smooth = TRUE, reg.line = TRUE, data = Data_BRICS)
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
scatterplot(DEPUB ~ Year | Country_Name, boxplot = FALSE,
            smooth = TRUE, reg.line = TRUE, data = Data_BRICS)
```

## 6. Model Specification OLS, Within, First difference, GLS

### 6.1 WAEMU Countries

We are going to regress economic growth per capita on the private investment,labor force, gross savings,public expenditure and public debts of the country. Model estimation using the `lm()` function

```{r echo=TRUE, message=FALSE, warning=FALSE}
reg1 <- lm(data = Data_UEMOA, GDP_Habitat ~ factor(Code) + POP_ACT + INPRIV + EPARBRUT + DEPUB + DEBTEXT)
summary(reg1)
```

Using `plm`, we can estimate the within model. Numerically equivalent to fixed effects.

```{r echo=TRUE, message=FALSE, warning=FALSE}
within_reg1 = plm(GDP_Habitat ~ POP_ACT + INPRIV + EPARBRUT + DEPUB + DEBTEXT, data=Data_UEMOA, model="within")
summary(within_reg1)
```

#Estimate the within model with two effects individuals and times

```{r echo=TRUE, message=FALSE, warning=FALSE}
within_reg1.tways = plm(GDP_Habitat ~ POP_ACT + INPRIV + EPARBRUT + DEPUB + DEBTEXT, data=Data_UEMOA, model="within", effect="twoways")
summary(within_reg1.tways)
```

#Estimate the pooling model

```{r echo=TRUE, message=FALSE, warning=FALSE}
pooling_reg1 = plm(GDP_Habitat ~ POP_ACT + INPRIV + EPARBRUT + DEPUB + DEBTEXT, data=Data_UEMOA, model="pooling")
summary(pooling_reg1)
```

We can also estimate the first difference model.

```{r echo=TRUE, message=FALSE, warning=FALSE}
fd_reg1 = plm(GDP_Habitat ~ POP_ACT + INPRIV + EPARBRUT + DEPUB + DEBTEXT, data=Data_UEMOA, model="fd")
summary(fd_reg1)
```

#### Fisher Test : Tests for individual and/or time effects

Before estimating the random effects model, we will check for the presence or absence of individual or time effects in our model using Fisher's test; we can also do this using the Breush-Pagan test, but it is the same thing.

```{r echo=TRUE, message=FALSE, warning=FALSE}
# The assumption of no individuals and times effects
pFtest(within_reg1.tways, pooling_reg1) 
```

The hypothesis of no individuals and times effects is strongly rejected with a p-value \< 2.2e-16 at 5%.

```{r echo=TRUE, message=FALSE, warning=FALSE}
# The assumption of no times effects, but assuming that there are individuals effects
pFtest(within_reg1.tways, within_reg1)
```

The hypothesis of no times effects, but assuming that there are individuals effects is strongly rejected with a p-value = 1.915e-05 at 5%. So the best within model is the model with two effects : individuals and times effects.

We can also estimate the random effect model with two effects.

```{r echo=TRUE, message=FALSE, warning=FALSE}
re_reg1 = plm(GDP_Habitat ~ POP_ACT + INPRIV + EPARBRUT + DEPUB + DEBTEXT, data=Data_UEMOA, effect="twoways", model="random")
summary(re_reg1)
```

### 6.2 BRICS Countries

Model estimation using the `lm()` function

```{r echo=TRUE, message=FALSE, warning=FALSE}
reg2 <- lm(data = Data_BRICS, GDP_Habitat ~ factor(Code) + POP_ACT + INPRIV + EPARBRUT + DEPUB + DEBTEXT)
summary(reg2)
```

Using `plm`, we can estimate the within model. Numerically equivalent to fixed effects.

```{r echo=TRUE, message=FALSE, warning=FALSE}
within_reg2 = plm(GDP_Habitat ~ POP_ACT + INPRIV + EPARBRUT + DEPUB + DEBTEXT, data=Data_BRICS, model="within")
summary(within_reg2)
```

#Estimate the within model with two effects individuals and times

```{r echo=TRUE, message=FALSE, warning=FALSE}
within_reg2.tways = plm(GDP_Habitat ~ POP_ACT + INPRIV + EPARBRUT + DEPUB + DEBTEXT, data=Data_BRICS, model="within", effect="twoways")
summary(within_reg2.tways)
```

#Estimate the pooling model

```{r echo=TRUE, message=FALSE, warning=FALSE}
pooling_reg2 = plm(GDP_Habitat ~ POP_ACT + INPRIV + EPARBRUT + DEPUB + DEBTEXT, data=Data_BRICS, model="pooling")
summary(pooling_reg2)
```

We can also estimate the first difference model.

```{r echo=TRUE, message=FALSE, warning=FALSE}
fd_reg2 = plm(GDP_Habitat ~ POP_ACT + INPRIV + EPARBRUT + DEPUB + DEBTEXT, data=Data_BRICS, model="fd")
summary(fd_reg2)
```

#### Fisher Test : Tests for individual and/or time effects

Before estimating the random effects model, we will check for the presence or absence of individual or time effects in our model using Fisher's test; we can also do this using the Breush-Pagan test, but it is the same thing.

```{r echo=TRUE, message=FALSE, warning=FALSE}
# The assumption of no individuals and times effects
pFtest(within_reg2.tways, pooling_reg2) 
```

The hypothesis of no individuals and times effects is strongly rejected with a p-value \< 7.678e-05 at 5%.

```{r echo=TRUE, message=FALSE, warning=FALSE}
# The assumption of no times effects, but assuming that there are individuals effects
pFtest(within_reg2.tways, within_reg2)
```

The hypothesis of no times effects, but assuming that there are individuals effects is not rejected with a p-value = 0.7135 at 5%. So the best within model is the model with only individuals effects.

```{r echo=TRUE, message=FALSE, warning=FALSE}
within_reg2.ind = plm(GDP_Habitat ~ POP_ACT + INPRIV + EPARBRUT + DEPUB + DEBTEXT, data=Data_BRICS, model="within", effect="individual")
summary(within_reg2.ind)
```

We can also estimate the random effect model. we can't use swar default random.method of error components model because the numbers of parameters included intercept is greater than the number of individus so we use the Amemiya random method with 3 degree of freedom which means that the unbiased version of the estimation of the error components is used.

```{r echo=TRUE, message=FALSE, warning=FALSE}
re_reg2 = plm(GDP_Habitat ~ POP_ACT + INPRIV + EPARBRUT + DEPUB + DEBTEXT, data=Data_BRICS,model="random", effect="individual",
              random.method = "amemiya", random.dfcor = 3)
summary(re_reg2)
```

## 7. Summary of estimated models

### 7.1 WAEMU Countries

```{r echo=TRUE, message=FALSE, warning=FALSE}
stargazer(reg1, fd_reg1, pooling_reg1, within_reg1.tways, re_reg1,
          dep.var.caption="",dep.var.labels="GDP per Capita",
          model.numbers = FALSE,
          column.labels = c("OLS","First difference","Pooling","Within twoways","GLS"),
          omit.table.layout = "n", star.cutoffs = NA,keep.stat=c("rsq","n"),no.space=TRUE,
          header=FALSE,
          keep=c("POP_ACT","INPRIV","EPARBRUT","DEPUB","DEBTEXT"),
          title="Summary of estimated models", type="text"
)
```

### 7.2 BRICS Countries

```{r echo=TRUE, message=FALSE, warning=FALSE}
stargazer(reg2, fd_reg2, pooling_reg2, within_reg2.ind, re_reg2, 
          dep.var.caption="",dep.var.labels="GDP per Capita",
          model.numbers = FALSE,
          column.labels = c("OLS","First difference","Pooling","Within individuals", "GLS"),
          omit.table.layout = "n", star.cutoffs = NA,keep.stat=c("rsq","n"),no.space=TRUE,
          header=FALSE,
          keep=c("POP_ACT","INPRIV","EPARBRUT","DEPUB","DEBTEXT"),
          title="Summary of estimated models", type="text"
)
```

## 8. Hausman-Taylor Test

### 8.1 WAEMU Countries

Implementing a Hausman-Taylor test. Under the null hypothesis of no correlation between the regressors and the individual effects `cov(alpha_i,x_it)=0`, the statistics is distributed as a Chi-2 with fives degrees of freedom.This hypothesis, with a p-value of 3.268e-16 is rejected at the 5% confidence level. We therefore return the model with the fixed effects. In this case, the Within estimator is BLUE and better than the GLS estimator which is not consistent.

```{r echo=TRUE, message=FALSE, warning=FALSE}
phtest(within_reg1.tways,re_reg1)
```

### 8.2 BRICS Countries

Implementing a Hausman-Taylor test. Under the null hypothesis of no correlation between the regressors and the individual effects `cov(alpha_i,x_it)=0`, the statistics is distributed as a Chi-2 with fives degrees of freedom because 5 parameters without alpha_i.This hypothesis, with a p-value of 0.7752 is not rejected at the 5% confidence level. We therefore return the random effects/Error Component Model.

```{r echo=TRUE, message=FALSE, warning=FALSE}
phtest(within_reg2.ind,re_reg2)
```

## Heteroscedasticity Test - Breush-Pagan Test

We performed the breush-Pagan test to test the presence of heteroscedasticity in the models retained in each group of countries. H0 : There is Homoscedasticity.

### WAEMU

```{r echo=TRUE, message=FALSE, warning=FALSE}
bptest(formula = within_reg1.tways , studentize = F)
```

This hypothesis, with p-value of 0.0001135 is rejected at the 5% confidence level. So there there is Heteroscedasticity in the fixed effect model.

### BRICS

```{r echo=TRUE, message=FALSE, warning=FALSE}
bptest(formula = re_reg2 , studentize = F)
```

This hypothesis, with p-value of 0.1905 is not rejected at the 5% confidence level. So there there is Homoscedasticity in the random effect model.

## Autocorrelation Test/serial correlation Durbin-Watson Test & Breusch-Godfrey/Wooldridge Test

The test of autocorrelation of errors is only done on the random effects model. And as it is the model used in the BRICS countries. So we will do this test on the random effects model of the BRICS countries. For this we performed serial correlation of Durbin-Watson.

H0 : There is no Autocorrelation in error term.

```{r echo=TRUE, message=FALSE, warning=FALSE}
pdwtest(re_reg2)
```

This hypothesis, with p-value of 0.0001135 is rejected at the 5% confidence level. So there there is Autocorrelation in error term of random effect model. This is perfectly normal as it is a spherical error model. To confirm this result. We performed Breusch-Godfrey/Wooldridge test for serial correlation in panel models. Which is test based on fixed effect model. And we have same result.

```{r echo=TRUE, message=FALSE, warning=FALSE}
pbgtest(within_reg2.ind)
```
